Extending K-Means Clustering with Ptolemy’s Inequality

### 2024-10-01 content/3u4_methods.tex
format

    \begin{equation*}
\begin{aligned}
\label{eq4.7}
    d(a,c') \cdot d(b,c) &\leq d(a, c) \cdot d(b, c') + d(a, b) \cdot d(c, c') \\
    d(a,c') &\leq \frac{d(a, c) \cdot d(b, c') + d(a, b) \cdot d(c, c')}{d(b,c)}
\end{aligned}
\end{equation*}
    By replacing some distances with upper boundaries you get the desired upper boundaries.
\end{proof}

@@

\begin{equation*}
\begin{aligned}
    d(x_i,c_i^{old}) &\leq u_i^{old}\\
    d(x_i,c_i^{old, old}) &\leq u_i^{old, old}
\end{aligned}
\end{equation*}

@@

\begin{equation*}
\begin{aligned}
    l_{i,j}^{\text{old}} &\leq d(x_i, c_j^{\text{old}}) \\
    l_{i,j}^{\text{old,old}} &\leq d(x_i, c_j^{\text{old,old}})
\end{aligned}
\end{equation*}

>>>>

	\begin{equation*}
		\begin{aligned}
			\label{eq4.7}
			d(a,c') \cdot d(b,c) & \leq d(a, c) \cdot d(b, c') + d(a, b) \cdot d(c, c')                \\
			d(a,c')              & \leq \frac{d(a, c) \cdot d(b, c') + d(a, b) \cdot d(c, c')}{d(b,c)}
		\end{aligned}
	\end{equation*}
	By replacing some distances with upper boundaries you get the desired upper boundaries.
\end{proof}

@@

\begin{equation*}
	\begin{aligned}
		d(x_i,c_i^{old})      & \leq u_i^{old}      \\
		d(x_i,c_i^{old, old}) & \leq u_i^{old, old}
	\end{aligned}
\end{equation*}

@@

\begin{equation*}
	\begin{aligned}
		l_{i,j}^{\text{old}}     & \leq d(x_i, c_j^{\text{old}})     \\
		l_{i,j}^{\text{old,old}} & \leq d(x_i, c_j^{\text{old,old}})
	\end{aligned}
\end{equation*}
